A Case Study in Preserving a High Energy Physics Application

### 2015-01-02 paper.tex
Revised Abstract

\begin{abstract}
\it The reproducibility of scientific results increasingly
depends upon the preservation of computational artifacts.
Although preserving a computation to be used later sounds
easy, it is surprisingly difficult due to the complexity
of existing software and systems.  Implicit dependencies,
networked resources, and shifting compatibility all conspire
to break applications that appear to work well.  To investigate
these issues, we present a case study of a complex high energy
physics application.  We analyze the application and attempt
several methods at extracting its dependencies for the purposes
of preservation. 
We propose one fine-grained dependency management toolkit to preserve the application and demonstrate its correctness in two different environments - one virtual machine from the Notre Dame Cloud Platform and one virtual machine from the Amazon EC2 Platform. 
We report on the completeness, performance,
and efficiency of each technique, and offer some guidance for
future work in application preservation.
\end{abstract}

>>>>

\begin{abstract}
\it Computational reproducibility depends on being able to isolate necessary and sufficient computational artifacts and preserve them for later re-execution.
Both isolation and preservation of artifacts can be challenging due to the complexity
of existing software and systems and the resulting implicit dependencies, resource distribution, and shifting compatibility of systems---all conspiring
to break the reproducibility of an application. Sandboxing is a technique
that has been used extensively in OS environments for isolation of computational artifacts.
Several tools were proposed recently that employ sandboxing as a mechanism to ensure reproducibility.
However, none of these tools preserve the sandboxed application for re-distribution
to a larger scientific community---aspects that are equally crucial for ensuring reproducibility as sandboxing itself.
In this paper, we describe a combined sandboxing and preservation framework, which is efficient and practical and
useful for large-scale reproducibility. We present a case study of a complex high energy
physics application and show how the framework can be useful for sandboxing and preserving.
We report on the completeness, performance,
and efficiency of the framework, and suggest possible standardization approaches.
\end{abstract}
